Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-12 shanghai.tex
Proved the second lemma in the section on finite geochars. It need polishing later.
That's all for tonight. Moving on to the section on restriction to the
identity component tomorrow.

\begin{proof}
Before compare $m^*(f,\psi)$ and 
\end{proof}

>>>>

\begin{proof}
As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$ where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
\[
\begin{tikzcd}
V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
\end{tikzcd}
\]
On the other hand, set $p_1^*(f,\psi) = (f_1,\psi_1)$, so $f_1 = f\times \id : H\times G\to G\times G$ and $A_1\ceq \ker f_1 = A \times G$ and $\psi_1 = \psi \circ p_1$; set $p_2^*(f,\psi) = (f_2,\psi_2)$, so $f_2 = \id \times f : G\times H \to G\times G$ and $A_2\ceq \ker f_2 = G \times A$ and $\psi_2 = \psi \circ p_2$. Then $(f,\psi) \boxtimes (f,\psi) = (f_1,\psi_1) \otimes (f_2,\psi_2) = (f_1\times_{G\times G} f_2, \psi_1\otimes \psi_2) = (f\times f, \psi\otimes \psi) $ is given by
\[
\begin{tikzcd}
V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes \psi} A \times A \arrow[hook]{r}{} & H \times H \arrow{r}{f\times f} & G\times G\\
\end{tikzcd}
\]
Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back, there is a unique $\theta : H\times H \to H_m$ making the following commute.
\[
\begin{tikzcd}
\ &  & \arrow{ld}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
V \arrow{d}{U} & \Aut(V)  & \arrow{l}{\psi_g} \arrow{u} A_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G\\
V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes\psi} \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta\vert_{A\times A}} A \times A \arrow[hook]{r}{} & \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta} H \times H \arrow{r}{f\times f} & \arrow[equal]{u} G\times G\\
\end{tikzcd}
\]
Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$. Define $U : V \to V\otimes V$ by $U(v_1) = v_1\otimes v_1$. Then the lower part of this diagram defines a weak isomorphism $(\theta,U): (f_m,\psi_m)\to (f\times f,\psi\otimes\psi)$. This defines an weak isomorphism $(\theta,U): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.

While $\theta$ was canonical, $U$ was not, as it depended on the choice of a basis for $V$. However, after passing from $C_1(G)$ to $\GCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\GCf(G)$.
\end{proof}
